Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-03-27 src/tex/ms.tex
Add kw comment
update

\usepackage{tabularx,booktabs,multirow}
\usepackage{float}
\usepackage[italicdiff]{physics}

%\definecolor{rb4}{HTML}{27408B}
%\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
%\newcommand{\kl}[1]{\color{cyan}[KL: #1 ]}
\newcommand{\ripple}{\texttt{ripple}}
\newcommand{\python}{\texttt{python}}
\newcommand{\jax}{\texttt{jax}}
\newcommand{\zdethp}{\texttt{zdethp}}

@@

% Waveform families and slight motivation of why we take Phenom model
Currently, three families of GW models are commonly used. They are the
effective-one-body (EOB) \citep{taracchini2014effective}, Numerical Relativity
(NR) surrogate \citep{varma2019surrogate} and phenomenological (Phenom) models
\citep{husa2016frequency,khan2016frequency} \kw{Add more citations related to
the newest models}. EOB models are constructed by mapping two masses onto an
effective body under an effective metric; NR surrogate models construct
waveforms using combinations of NR waveforms; Phenom models are formulated using
specific ansatz and inspiral approximations. While EOB and NR surrogate models
give better waveform approximants, Phenom waveforms can be produced much faster,
hence it is used mostly in data analysis tasks that requires many waveform
generations. This advantage scales up in data analysis tasks such as matched
filtering and parameter estimation, where many waveforms are required in each
run. This motivates us to improve upon the current framework of Phenom models,
thus can retain the advantage of fast waveform generation while improving the
model's accuracy.

@@

In order to recalibrate the model, we have to understand what parameters the model has.
Here we give a succinct summary of the IMRPhenomD model and the relevant parameters.
For interested readers, please refer to \cite{khan2016frequency} for more details on construction of the model.

The IMRPhenomD model is constructed by combining three individually fitted parts
into one coherent waveform model, which consists of the inspiral, intermediate, and merger-ringdown part, 
\kw{Check if the following equation is correct. I think it is off by some smoothing factors.}
\begin{align}
	h(f,\theta)&=h_{\mathrm{ins}}(f,\theta) + h_{\mathrm{int}}(f,\theta) + h_{\mathrm{me-rd}}(f,\theta).
\end{align}

Instead of fitting the strain, which is a highly oscillatory function that is
difficult to fit, the amplitude and phase are fitted since they are smoother
functions. In each part, the amplitude and phase are made using simple functions
of frequency such as polynomials or lorentzians. These simple analytic functions
consists of parameters $\Lambda^i$, which are defined as follows. \kw{Can you
change equation one such that it consists of $\Lambda$? Also be explicit about
the form of the function used for the fitting. Like write down the polynomials
and lorentizans for the specific parts.}
\begin{align} \label{eq:Lambda}
	\Lambda^i&=\lambda_{00}^i+\lambda_{10}^i\eta \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)(\lambda_{01}^i+\lambda_{11}^i\eta+\lambda_{21}^i\eta^2) \nonumber \\ 
	&+(\chi_{\mathrm{PN}}-1)^2(\lambda_{02}^i+\lambda_{12}^i\eta+\lambda_{22}^i\eta^2) \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)^3(\lambda_{03}^i+\lambda_{13}^i\eta+\lambda_{23}^i\eta^2),
\end{align}
where $\lambda$ are fitting coefficients obtained during calibration, $\eta$ is
the symmetric mass ratio, and $\chi_{\mathrm{PN}}$ is the post-Newtonian spin
parameter, which is defined as 
\begin{align}
	\chi_{\mathrm{PN}}=\frac{m_1\chi_1+m_2\chi_2}{m_1+m_2}-\frac{38\eta}{113}(\chi_1+\chi_2).
\end{align}
Here, $m_{1,2}$ and $\chi_{1,2}$ are the primary and secondary mass and spin,
respectively. Finally, the individual segments are connected in a way that the
final waveform is continuous in its first derivative \kw{expand a bit}.

\kw{Need to work on this paragraph}
From Eq. \ref{eq:Lambda}, we can see that the values of $\lambda$ are
fundamental to waveform generation, which can significantly affect the shape of
final waveforms. Thus, having a set of accurate waveform coefficients is
important. Generally, waveform coefficients are obtained by calibrating with NR
waveforms, which are waveforms computed using NR simulations. In the case of
\citep{khan2016frequency}, $\lambda$ were obtained by fitting model-generated
waveforms to NR waveforms. For each NR simulation, they can obtain one set of
$\Lambda$'s through optimization. With many sets of $\Lambda$, $\lambda$ are
subsequently found by fitting against Eq. \ref{eq:Lambda}. Since the fitting
procedure is done in a piece-wise manner, the correlations between different
segments are omitted, which could limit the accuracy of the model. Also,
their calibration procedure does not guarantee to have the optimal set of
$\lambda$, since the process of connecting segments alters the previously fitted
waveform. The model-generated waveforms do not take this effect into account,
and thus introduces additional inaccuracies.

% they did not use mismatch as the loss function

@@

\subsection{Mismatch} \label{subsec:mismatch}

@@

\kw{Remind me why don't we use the hybrid waveforms again? Cause we couldn't do it?}
In the original calibration \citep{khan2016frequency,husa2016frequency},
training waveforms are hybrid waveforms of NR simulations and SpinAlignedEOB
(SEOB) waveforms. The low frequency inspiral part is taken from the SEOB
waveforms while the rest of the waveforms are taken from NR simulations.
Instead, we solely use NR waveforms for comparison, since most NR waveforms used
have long enough time series data, i.e.~$>15$ orbits \citep{boyle2019sxs}, in
which they are long enough to contain part of the inspiral segment and all
merger and ringdown frequency information. We take the frequency limits as
$f_{\mathrm{min}}=0.1f_{\mathrm{RD}}$ and $f_{\mathrm{max}}=1.2f_{\mathrm{RD}}$,
where $f_{\mathrm{RD}}$ is the frequency at ringdown. This range covers most of
the IMRPhenomD's frequency range, except the minimum frequency is set higher
than that in the original calibration due to NR length. When compared with
IMRPhenomC, the frequency range is slightly extended to have a higher maximum
frequency.

To compute the integral shown in Eq. \ref{eq:inner_prod}, one need to choose a
relevant noise PSD. Since a common goal for creating waveform approximent is to
deploy the waveform model in downstream data analysis tasks, a reasonable choice
for the noise PSD should be closely related to the instrument of interest. We
choose the zero-detuned high-power (\zdethp) noise PSD \kw{add citation} as our
first choice of noise PSD. Because the total mass of the system simple scales
the frequency of the waveform, we need to choose a corresponding mass scale to
match the frequency range of our noise PSD. Here, we choose $M=50M_{\odot}$ for
all waveforms, since this mass scale is common in LIGO observations. In addition
to a detector-dependent PSD, we are also interested in a more
instrument-agnostic case such that we can evaluate the effectiveness of the
recalibration without considering detector effect. In this case, we set the
noise PSD to be a constant value.

% GW strain treatment from time-series to frequency domain
In our work, mismatches are used as a measure of discrepancies between
IMRPhenomD waveforms and NR waveforms. To compute such mismatches, NR waveforms
from the SXS catalog are taken \citep{boyle2019sxs}. These NR waveforms are
calculated using the \texttt{SpEC} code. Initially, NR waveforms are in the form
of time-series data. Since time-series data is oscillatory, performing
optimization in the time-domain is not ideal. Hence, we had chosen to transform
NR waveforms to frequency-domain to compare with IMRPhenomD waveforms with the
same intrinsic parameters. We taper the time-series using Tukey window.
\footnote{ Specifically, we choose $\alpha=2t_{\mathrm{RD}}/T$, where
$t_{\mathrm{RD}}$ is the duration of ringdown and $T$ is the duration of the
entire BBH event. } Then, the frequency spectra can be obtained by taking the
Fourier transform of the time-series. Then, mismatches can be calculated through
Eq.~\ref{eq:mismatch}~and~\ref{eq:inner_prod}.

@@

Using \ripple, we can make use of {\jax} to evaluate gradients accurately. Thus,
we can utilize simple gradient descent to recalibrate the model.

% \kw{Mention the main advantage in this study is we can optimize everything at
% once.}

% To recalibrate the model, we have to define loss functions that quantify the
% difference between the model-generated waveforms and NR waveforms. In the
% original calibration, they took the mean square error as the loss function for
% optimization. Instead, we directly use mismatch as our metric for loss
% functions. However, the mismatch of individual waveforms is not useful in
% optimization, since it does not represent all waveforms with various intrinsic
% parameters. We ought to calibrate coefficients that suit waveforms with
% different intrinsic parameters simultaneously, hence waveforms in different
% regions of parameter space should be used in the optimization scheme. Here, we
% chose two different loss functions to examine their ability to optimize the
% model, e.g. mean of individual mismatches $\mathcal{L}_{\mathrm{mean}}$ and
% fractional loss $\mathcal{L}_{\mathrm{fl}}$.

% Do something much more direct:
To recalibrate the model, we need to define a loss function that quantifies the
difference between the model-generated waveforms and NR waveforms. We use
mismatch over the set of all training waveforms as the loss function. While in
\citep{khan2016frequency}, they chose to use the mean square error as the loss
function, we choose mismatch as the loss function because it is closely related
to downstream objectives such as the likelihood in parameter estimation. The
mismatch is averaged over the training dataset in two ways to cover the
parameter space of interest. One of which takes a simple average and the other
takes a normalized average based on initial mismatch.

% To recalibrate the model, we need to define a loss function that quantify ...
% We use mismatch over the set of all training waveforms as the loss function.
% We choose mismatch as the loss function because it is closely related to
% downstream objectives such as the likelihood in parameter estimation. The
% mismatch is averaged over the training dataset to cover the parameter space of
% interest. (used)
\begin{align}
	\mathcal{L}_{\mathrm{mean}}&=\frac{1}{N}\sum_{i=1}^N\mathcal{M}_i \\
	\mathcal{L}_{\mathrm{fl}}&=\frac{1}{N}\sum_{i=1}^N\frac{\mathcal{M}_i}{\mathcal{M}_{i,\mathrm{ini}}},
\end{align}	
$\mathcal{M}_i$ represents the mismatch of an individual training waveform,
$\mathcal{M}_{i,\mathrm{ini}}$ represents the initial mismatch of the individual
training waveform, and $N$ is the total number of individual training waveforms.
For the first choice, it takes the mean of the mismatches, which serves as a
basic loss function. However, it is prone to be dominated by a single waveform
with a large mismatch. Other waveforms with smaller mismatches would be
insignificant comparatively, and might not be able to improve under such
optimization. Alternatively, the second choice, the mean of normalized
mismatches, eliminates the aforementioned issue. Nevertheless, it excludes the
information on initial mismatches. $\mathcal{L}_{\mathrm{fl}}$ restricts every
training waveform to decrease at similar rates, hence it is hard to obtain
optimized waveforms with mismatches in the same order of magnitude. Instead,
their ratios in mismatches would remain approximately the same. Conversely,
$\mathcal{L}_{\mathrm{mean}}$ allows the loss function to automatically adjust
and final individual mismatches would be in a similar order of magnitude. In
this paper, we display the results of using both loss functions and examine the
difference between them.

We have chosen 11-16 NR waveforms from the set of waveforms used in the original
calibration process. Originally, 19 waveforms are taken from NR simulations for
calibrating IMRPhenomD \citep{khan2016frequency,husa2016frequency}, which they
are waveforms from the SXS catalog or BAM simulation. As BAM waveforms are not
publicly available, we cannot take the identical training set as them. Instead,
we take the available waveforms from the SXS catalog to construct our loss
function. They are listed in Tab.~\ref{tab:q148}~and~\ref{tab:q1248}. Notice the
maximum mass ratio in our training set is lower than that in
\citep{khan2016frequency}. Instead of having $q\leq18$, the maximum mass ratio
is set as 8. This is because SXS catalog does not have NR waveforms with
extremely high mass ratio. In fact, the SXS catalog only has NR waveforms with
$q\leq10$. Nevertheless, we are interested in the behavior of IMRPhenomD model
with small $q$, as most BBH events observed have $q\leq8$. Hence, we set the
maximum mass ratio to 8.

With both mismatches, we apply gradient descent to optimize the tunable
coefficients as follows: 
\begin{algorithm}
	\caption{Gradient descent pseudocode}
	\KwIn{initial coefficients $\lambda_i$} \Parameters{number of iterations
	$N$, learning rate $\alpha$} \Variables{current coefficients $\lambda$,
	mismatch gradient $\nabla\mathcal{L}$} \KwResult{output coefficients
	$\lambda$} $\lambda\leftarrow\lambda_i$\\
	\tcc{Gradient Descent}
	\For{$i<N$}{ $\mathcal{L}\leftarrow Mismatch(\lambda)$ \\
		$\nabla\mathcal{L}\leftarrow AutoDiff(\mathcal{L})$\\
		$\lambda\leftarrow\lambda-\alpha\nabla\mathcal{L}$\\
	} \Return{$\lambda$}
\end{algorithm}
Here, $\lambda_i$ are the original coefficients given in
\citep{khan2016frequency}. We take them as the initial waveform coefficients
because they lie in the neighborhood of the minimum that we wish to find. With
such an optimization procedure, we obtain the optimized coefficients.

>>>>

\usepackage{tabularx,booktabs,multirow,amsmath}
\usepackage{float}
\usepackage[italicdiff]{physics}

%\definecolor{rb4}{HTML}{27408B}
%\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
%\newcommand{\kl}[1]{\color{cyan}[KL: #1 ]}
\newcommand{\ripple}{\texttt{ripple}}
\newcommand{\python}{\texttt{python}}
\newcommand{\jax}{\texttt{jax}}
\newcommand{\zdethp}{\texttt{zdethp}}
\definecolor{rb4}{HTML}{27408B}
\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
\definecolor{cyan}{HTML}{0097A7}
\newcommand{\kl}[1]{{\color{cyan}[KL: #1 ]}}

@@

% Waveform families and slight motivation of why we take Phenom model
Currently, three families of GW models are commonly used. They are the
effective-one-body (EOB) \citep{ossokine2020multipolar, cotesta2020frequency, taracchini2014effective}, Numerical Relativity
(NR) surrogate \citep{islam2022surrogate, varma2019surrogate, varma2019surrogate2} and phenomenological (Phenom) models
\citep{husa2016frequency, khan2016frequency, garcia2020multimode, pratten2021computationally} \kw{Add more citations related to
the newest models}. EOB models are constructed by mapping two masses onto an
effective body under an effective metric; NR surrogate models construct
waveforms using combinations of NR waveforms; Phenom models are formulated using
specific ansatz and inspiral approximations. While EOB and NR surrogate models
give better waveform approximants, Phenom waveforms can be produced much faster,
hence it is used mostly in data analysis tasks that requires many waveform
generations. This advantage scales up in data analysis tasks such as matched
filtering and parameter estimation, where many waveforms are required in each
run. This motivates us to improve upon the current framework of Phenom models,
thus can retain the advantage of fast waveform generation while improving the
model's accuracy.

@@

In order to recalibrate the model, we have to understand what parameters the model has.
Here we give a succinct summary of the IMRPhenomD model and the relevant parameters.
For interested readers, please refer to \citep{khan2016frequency} for more details on construction of the model.

The IMRPhenomD model is constructed by combining three individually fitted parts
into one coherent waveform model, which consists of the inspiral, intermediate, and merger-ringdown part, 
\kw{Check if the following equation is correct. I think it is off by some smoothing factors.} 
\kl{I don't remember there is any smoothing factors. They are just connected using step functions, then the entire waveform is made to have continuous first derivative by fixing some of the coefficients for the two connections.}
\begin{align}\label{eq:joint_waveform}
	h(f,\theta,\Lambda^i)=h_{\mathrm{ins}}(f,\theta,\Lambda^i) + h_{\mathrm{int}}(f,\theta,\Lambda^i) + h_{\mathrm{rd}}(f,\theta,\Lambda^i).
\end{align}

Instead of fitting the strain, which is a highly oscillatory function that is
difficult to fit, the amplitude and phase are fitted since they are smoother
functions. In each part, the amplitude and phase are made using simple functions
of frequency such as polynomials or lorentzians. Specifically, the merger-ringdown amplitude is fitted by a lorentzian and the other parts are fitted using polynomials. 
\begin{equation}\label{eq:amplitude}
\begin{aligned}
	A_0&\equiv\sqrt{\frac{2\eta}{3\pi^{1/3}}}f^{-7/6}\\
	A_{\mathrm{ins}}(f;\theta)&=A_{\mathrm{PN}}(f;\theta)+A_0\sum_{i=1}^3\rho_if^{(6+i)/3} \\
	A_{\mathrm{int}}(f;\theta)&=A_0(\delta_0+\delta_1f+\delta_2f^2+\delta_3f^3+\delta_4f^4) \\
	A_{\mathrm{rd}}(f;\theta)&=A_0\left[\gamma_1\frac{\gamma_3f_{\mathrm{damp}}}{(f-f_{\mathrm{RD}})^2+(\gamma_3f_{\mathrm{damp}})^2}e^{-\frac{\gamma_2(f-f_{\mathrm{RD}})}{\gamma_3f_{\mathrm{damp}}}}\right],  
\end{aligned}
\end{equation}
where $A_{\mathrm{PN}}$ is the post-newtonian expansion of the insprial amplitude up to order $A_0f^2$, $f_{\mathrm{damp}}$ is the damping frequency, and $f_{\mathrm{RD}}$ is the frequency at ringdown. The ansatzes for phase can be found in \citep{khan2016frequency}. These simple analytic functions
consists of parameters $\Lambda^i=\{\rho_i,\delta_i,\gamma_i\}$, which are defined as follows. \kw{Can you
change equation one such that it consists of $\Lambda$? Also be explicit about
the form of the function used for the fitting. Like write down the polynomials
and lorentizans for the specific parts.}
\begin{align} \label{eq:Lambda}
	\Lambda^i&=\lambda_{00}^i+\lambda_{10}^i\eta \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)(\lambda_{01}^i+\lambda_{11}^i\eta+\lambda_{21}^i\eta^2) \nonumber \\ 
	&+(\chi_{\mathrm{PN}}-1)^2(\lambda_{02}^i+\lambda_{12}^i\eta+\lambda_{22}^i\eta^2) \nonumber \\
	&+(\chi_{\mathrm{PN}}-1)^3(\lambda_{03}^i+\lambda_{13}^i\eta+\lambda_{23}^i\eta^2),
\end{align}
where $\lambda$ are fitting coefficients obtained during calibration, $\eta$ is
the symmetric mass ratio, and $\chi_{\mathrm{PN}}$ is the post-Newtonian spin
parameter, which is defined as 
\begin{align}
	\chi_{\mathrm{PN}}=\frac{m_1\chi_1+m_2\chi_2}{m_1+m_2}-\frac{38\eta}{113}(\chi_1+\chi_2).
\end{align}
Here, $m_{1,2}$ and $\chi_{1,2}$ are the primary and secondary mass and spin,
respectively. Finally, the individual segments are first connected directly using 
step functions. Then, by fixing coefficients in the intermediate waveform, one can make 
the final waveform is continuous in its first derivative \kw{expand a bit}.

\kw{Need to work on this paragraph}
Combining Eq.~\ref{eq:joint_waveform},~\ref{eq:amplitude}~and~\ref{eq:Lambda}, 
we can see that the entire waveform is non-linear in $\lambda$. A slightly 
inaccurate set of $\lambda$ can significantly affect the shape of the generated 
waveforms. Thus, having a set of accurate waveform coefficients is important 
and fundamental to having accurate GW models. Generally, waveform coefficients 
are obtained by calibrating with NR waveforms, which are waveforms computed 
using NR simulations. In the case of \citep{khan2016frequency}, they first 
obtain a set of $\Lambda$ by fitting model generated waveforms to Eq.~\ref{eq:amplitude} 
and the phase ansatzes. Repeating with different NR waveforms, they obtain multiple 
sets of $\Lambda$, and $\lambda$ are subsequently found by fitting against 
Eq. \ref{eq:Lambda}. Since the fitting procedure is done in a piece-wise manner, 
the correlations between different segments are omitted, which could limit the 
accuracy of the model. Also, since fitting was performed before connecting 
individual segments, the final waveform does not guarantee to achieve the optimal 
waveform. The connecting procedure can alter the previously fitted waveform. 
Hence, the model generated waveforms contains additional inaccuracies.

%their calibration procedure does not guarantee to have the optimal set of
%$\lambda$, since the process of connecting segments alters the previously fitted
%waveform. The model-generated waveforms do not take this effect into account,
%and thus introduces additional inaccuracies.

@@

\subsection{Loss Function} \label{subsec:loss}

@@

Since we wish to optimize the model over the whole parameter space, we need to compare multiple model generated waveforms with NR waveforms. However, mismatch only quantifies the difference between IMRPhenomD and NR waveform for one particular set of intrinsic parameters. To take into account of various different waveforms in the parameter space, we pick waveforms from the different parts of the parameter space. We define the loss function as an average of training waveforms in two ways, the simple average of mismatches and the normalize average of mismatches,  
\begin{align}
	\mathcal{L}_{\mathrm{mean}}&=\frac{1}{N}\sum_{i=1}^N\mathcal{M}_i \\
	\mathcal{L}_{\mathrm{fl}}&=\frac{1}{N}\sum_{i=1}^N\frac{\mathcal{M}_i}{\mathcal{M}_{i,\mathrm{ini}}},
\end{align}	
where $\mathcal{M}_i$ represents the mismatch of an individual training waveform,
$\mathcal{M}_{i,\mathrm{ini}}$ represents the initial mismatch of the individual
training waveform, and $N$ is the total number of individual training waveforms.
Note that we choose to use two different averages, since they have different 
preferences in optimization base on waveform mismatches. For the first choice, simple average serves as the simplest choice of loss function, but is prone to be dominated by a single waveform with a large mismatch. Other waveforms with smaller mismatches would be
insignificant comparatively, and might not be able to improve under such
optimization. Alternatively, the second choice, normalized average eliminates the aforementioned issue. Nevertheless, it excludes the
information on initial mismatches. $\mathcal{L}_{\mathrm{fl}}$ restricts every
training waveform to decrease at similar rates, hence it is hard to obtain
optimized waveforms with mismatches in the same order of magnitude. Instead,
their ratios in mismatches would remain approximately the same. Conversely,
$\mathcal{L}_{\mathrm{mean}}$ allows the loss function to automatically adjust
and individual mismatches would be in a similar order of magnitude after 
optimization. In this paper, we showcase the results of using both loss functions 
and examine the differences between them.

@@

To compute the loss functions, we have to take NR waveforms for calculating the mismatch. We choose 11-16 NR waveforms from the set of waveforms used in the original
calibration process as training waveforms. Originally, 19 waveforms are taken from 
NR simulations for calibrating IMRPhenomD \citep{khan2016frequency}, 
which are waveforms from the SXS catalog \citep{boyle2019sxs} or BAM simulation. 
As BAM waveforms are not publicly available, we cannot take the identical training 
set as them. Instead, we take the available waveforms from the SXS catalog to construct our loss function. Training waveforms used are listed in Tab.~\ref{tab:q148}~and~\ref{tab:q1248}. The training waveforms chosen has maximum mass ratio to be 8. This is because SXS catalog does not have NR waveforms with extremely high mass ratio. In fact, the SXS catalog only has NR waveforms with $q\leq10$. Nevertheless, we are interested in the behavior of IMRPhenomD model with small $q$, as most BBH events observed from LIGO have $q\leq8$. Hence, we calibrate IMRPhenomD with waveforms of $q\leq8$.

In the SXS catalog, NR waveforms are in the form of time-series strain. Since time-series data is oscillatory, performing optimization in the time-domain is not ideal. Hence, we transform NR waveforms to frequency-domain to compare with IMRPhenomD waveforms with the
same intrinsic parameters. We taper the time-series using Tukey window.
\footnote{ Specifically, we choose $\alpha=2t_{\mathrm{RD}}/T$, where
	$t_{\mathrm{RD}}$ is the duration of ringdown and $T$ is the duration of the
	entire GW strain. } 
Then, the frequency spectra can be obtained by taking the Fourier transform of the time-series.

Other than NR waveforms, one need to choose a relevant noise PSD for 
mismatch. Since a common goal for creating waveform approximant is to
deploy the waveform model in downstream data analysis tasks, a reasonable choice
for the noise PSD should be closely related to the instrument of interest. We
choose the zero-detuned high-power (\zdethp) noise PSD as our
first choice of noise PSD \citep{aasi2015advanced}. Because the total mass of the system simple scales
the frequency of the waveform, we need to choose a corresponding mass scale to
match the frequency range of our noise PSD. Here, we choose $M=50M_{\odot}$ for
all waveforms, since this mass scale is common in LIGO observations. In addition
to a detector-dependent PSD, we are also interested in a more
instrument-agnostic case such that we can evaluate the effectiveness of the
recalibration without considering detector effect. In this case, we set the
noise PSD to be a constant value.

\kw{Remind me why don't we use the hybrid waveforms again? Cause we couldn't do it?}
We shall notify readers that our treatment to NR waveforms is different from that of \citep{husa2016frequency, khan2016frequency}. In the original calibration process, training waveforms are hybrid waveforms of NR and SpinAlignedEOB
(SEOB) waveforms. The low frequency inspiral part is taken from the SEOB
waveforms while the rest of the waveforms are taken from NR simulations.
Instead, we solely use NR waveforms for comparison, since we only exploring the possibility of optimizing waveform models. Thus, for simplicity sake, we ignore this procedure. On the other hand, most NR waveforms used (for both training and testing) have long enough time series data, i.e.~$>15$ orbits \citep{boyle2019sxs}, in
which they are long enough to contain part of the inspiral segment and all
merger and ringdown frequency information. We take the frequency limits as
$f_{\mathrm{min}}=0.1f_{\mathrm{RD}}$ and $f_{\mathrm{max}}=1.2f_{\mathrm{RD}}$,
where $f_{\mathrm{RD}}$ is the frequency at ringdown. This range covers most of
the IMRPhenomD's frequency range, except the minimum frequency is set higher
than that in the original calibration due to NR length. When compared with
IMRPhenomC, the frequency range is slightly extended to have a higher maximum
frequency.

With the loss function evaluated, we apply gradient descent to optimize the tunable
coefficients as shown in Algorithm~\ref{alg:gradient}. We take $\lambda_i$ to be the original coefficients given in \citep{khan2016frequency}. We take them as the initial waveform coefficients because they lie in the neighborhood of the minimum that we wish to find. With
such an optimization procedure, we can systematically obtain the optimized coefficients.

\begin{algorithm}[t]
	\caption{Gradient descent pseudocode}
	\label{alg:gradient}
	\KwIn{initial coefficients $\lambda_i$} \Parameters{number of iterations
		$N$, learning rate $\alpha$} \Variables{current coefficients $\lambda$,
		mismatch gradient $\nabla\mathcal{L}$} \KwResult{output coefficients
		$\lambda$} $\lambda\leftarrow\lambda_i$\\
	\tcc{Gradient Descent}
	\For{$i<N$}{ $\mathcal{L}\leftarrow Mismatch(\lambda)$ \\
		$\nabla\mathcal{L}\leftarrow AutoDiff(\mathcal{L})$\\
		$\lambda\leftarrow\lambda-\alpha\nabla\mathcal{L}$\\
	} \Return{$\lambda$}
\end{algorithm}
